\documentclass[PICOReport.tex]{subfiles}

\begin{document}
%
% author list table.
% 4 columns, authors + affiliations
%
%\LARGE{ \centerline{\bf{The Probe of Inflation and Cosmic Origins}}}
%
%
%% 1/7/2018. KY reduced font size to fit all Authors/Endorsers on 1 page. May make more sense to keep large size and
%% make the EC smaller or an * after names.  Also removed PICO title.
%\LARGE{ \centerline{The Probe of Inflation and Cosmic Origins}}
%\vskip -16pt
\LARGE{ \centerline{Report from a Probe-Scale Mission Study}}
\Large{ \centerline{January, 2019 }}
\vspace{5pt}

\parindent = 0pt
%\normalsize{
\small{
Principal Investigator: Shaul Hanany\,$^{48}$ } \\
\vspace{-6pt} \\
%\normalsize{
\small{
Steering Committee: Charles Bennett\,$^{23}$, Scott Dodelson\,$^{5}$, Lyman Page\,$^{31}$ } \\
\vspace{-6pt} \\
%\normalsize{
\small{
\raggedright
Executive Committee:
James~Bartlett\,$^{1,22}$,
Nick~Battaglia\,$^{8}$,
Jamie~Bock\,$^{2,22}$,
Julian~Borrill\,$^{26,37}$,
David~Chuss\,$^{53}$,
Brendan~P.~Crill\,$^{22}$,
Jacques~Delabrouille\,$^{1,20}$,
Mark~Devlin\,$^{50}$,
Laura~Fissel\,$^{29}$,
Raphael~Flauger\,$^{43}$,
Dan~Green\,$^{41}$,
J.~Colin~Hill\,$^{6,17}$,
Johannes~Hubmayr\,$^{28}$,
William~Jones\,$^{31}$,
Lloyd~Knox\,$^{42}$,
Al~Kogut\,$^{27}$,
Charles~Lawrence\,$^{22}$,
Jeff~McMahon\,$^{47}$,
Tim~Pearson\,$^{2}$,
Clem~Pryke\,$^{48}$,
Marcel~Schmittfull\,$^{17}$,
Amy~Trangsrud\,$^{22}$,
Alexander~van~Engelen\,$^3$ 
\\
}
\label{authorlist}

\vspace{9pt}

\Large  {\centerline {Authors}}
%
\footnotesize {
% change to left justified
\begin{multicols}{4}
%Marcelo Alvarez $^{26}$                \\
Marcelo Alvarez $^{26,41}$                 \\
Emmanuel Artis $^{20}$                  \\
%Peter Ashton $^{25}$                   \\
%Peter Ashton $^{26}$                   \\
Peter Ashton $^{25,26,41}$                    \\
Jonathan Aumont $^{19}$                 \\
Ragnhild Aurlien $^{49}$                 \\
Ranajoy Banerji $^{49}$                 \\
R. Belen Barreiro $^{18}$               \\
James G. Bartlett $^{1,22}$               \\
%James G. Bartlett $^{22}$              \\
Soumen Basak $^{34}$                    \\
Nick Battaglia $^{8}$                  \\
%Charles Bennett $^{23}$                \\
Jamie Bock $^{2,22}$                      \\
Kimberly K. Boddy $^{23}$               \\
Matteo Bonato $^{13}$                   \\
Julian Borrill $^{26,37}$                  \\
%Julian Borrill $^{37}$                 \\
Fran\c{c}ois Bouchet $^{15}$            \\
Fran\c{c}ois Boulanger $^{10}$          \\
Blakesley Burkhart $^{32}$              \\
Jens Chluba $^{21}$                     \\
David Chuss $^{53}$                     \\
Susan E. Clark $^{17}$                  \\
Joelle Cooperrider $^{22}$              \\
Brendan P. Crill $^{22}$                \\
Gianfranco De Zotti $^{14}$             \\
Jacques Delabrouille $^{1,20}$            \\
%Jacques Delabrouille $^{20}$           \\
%Mark  Devlin $^{50}$                   \\
Eleonora Di Valentino $^{46}$           \\
Joy Didier $^{51}$                      \\
%Scott Dodelson $^{5}$                 \\
Olivier Dor\'e $^{22,2}$                  \\
Hans K. Eriksen $^{49}$                 \\
Josquin Errard $^{1}$                  \\
Tom Essinger-Hileman $^{27}$            \\
Stephen Feeney $^{6}$                  \\
Jeffrey Filippini $^{45}$               \\
Laura Fissel $^{29}$                    \\
Raphael Flauger $^{43}$                 \\
Vera Gluscevic $^{44}$                  \\
Kris Gorski $^{22}$                     \\
Dan Green $^{41}$                       \\
Shaul Hanany $^{48}$                    \\
Brandon Hensley $^{31}$                 \\
Diego Herranz $^{18}$                   \\
J. Colin Hill $^{6,17}$                   \\
%J. Colin Hill $^{17}$                  \\
Eric Hivon $^{15}$                      \\
Ren\'{e}e  Hlo\v{z}ek $^{9}$           \\
Johannes Hubmayr $^{28}$                \\
Bradley R. Johnson $^{7}$              \\
William Jones $^{31}$                   \\
Terry Jones $^{48}$                     \\
Lloyd Knox $^{42}$                      \\
Al Kogut $^{27}$                        \\
Marcos L\'{o}pez-Caniego $^{11}$        \\
Charles Lawrence $^{22}$                \\
Alex Lazarian $^{52}$                   \\
Zack Li $^{31}$                         \\
Mathew Madhavacheril $^{31}$            \\
%Jeff McMahon $^{47}$                   \\
Jean-Baptiste Melin $^{20}$             \\
Joel Meyers $^{36}$                     \\
Calum Murray $^{1}$                    \\
Mattia Negrello $^{4}$                 \\
Giles Novak $^{30}$                     \\
Roger O'Brient $^{22,2}$                  \\
%Lyman Page $^{31}$                     \\
Christopher Paine $^{22}$               \\
Tim Pearson $^{2}$                     \\
Levon Pogosian $^{35}$                  \\
Clem Pryke $^{48}$                      \\
%Giuseppe Puglisi $^{24}$               \\
Giuseppe Puglisi $^{24,38}$                \\
Mathieu Remazeilles $^{21}$             \\
Graca Rocha $^{22}$                     \\
Marcel Schmittfull $^{17}$              \\
Douglas Scott $^{40}$                   \\
Peter Shirron $^{27}$                   \\
Ian Stephens $^{12}$                    \\
Brian Sutin $^{22}$                     \\
Maurizio Tomasi $^{39}$                 \\
Amy Trangsrud $^{22}$                   \\
Alexander van Engelen $^{3}$           \\
Flavien Vansyngel $^{16}$               \\
Ingunn K. Wehus $^{49}$                 \\
Qi Wen $^{48}$                          \\
Siyao Xu $^{52}$                        \\
Karl Young $^{48}$                      \\
Andrea Zonca $^{33}$
\end{multicols}
}

\Large { \centerline {Endorsers}}
%
\footnotesize {
%\begin{minipage}{1.2\textwidth}
\begin{multicols}{4}  
Maximilian Abitbol              \\
Zeeshan Ahmed                   \\
David Alonso                    \\
Jason Austermann                \\
Carlo Baccigalupi               \\
Darcy Barron                    \\
Daniel Baumann                  \\
Karim Benabed                   \\
Bradford Benson                 \\
Paolo de Bernardis              \\
Marco Bersanelli                \\
Federico Bianchini              \\
Colin Bischoff                  \\
Sebastian Bocquet               \\
J. Richard Bond                 \\
Jeffrey Booth                   \\
Sean Bryan                      \\
Carlo Burigana                  \\
Robert Caldwell                 \\
Xingang Chen                    \\
Francis-Yan Cyr-Racine          \\
Tijmen de Haan                  \\
Cora Dvorkin                    \\
Ivan Soares Ferreira            \\
Aurelien Fraisse                \\
Andrei V. Frolov                \\
Ken Ganga                       \\
Silvia Galli                    \\
Ken Ganga                       \\
Tuhin Ghosh                     \\
Sunil Golwala                   \\
Riccardo Gualtieri              \\
Jon E. Gudmundsson              \\
Nikhel Gupta                    \\
Sophie Henrot-Versill\'e        \\
Thiem Hoang                     \\
Kevin M. Huffenberger           \\
Marc Kamionkowski               \\
Reijo Keskitalo                 \\
Rishi Khatri                    \\
Theodore Kisner                 \\
Arthur Kosowsky                 \\
Ely Kovetz                      \\
Kerstin Kunze                   \\
Guilaine Lagache                \\
Daniel Lenz                     \\
Fran\c{c}ois Levrier            \\
Marilena Loverde                \\
Philip Lubin                    \\
Juan Macias-Perez               \\
Nazzareno Mandolesi             \\
Enrique Mart\'{i}nez-Gonz\'{a}lez   \\
Carlos Martins                  \\
Silvia Masi                     \\
Tomotake Matsumura              \\
P. Daniel Meerburg              \\
Amber Miller                    \\
Lorenzo Moncelsi                \\
Pavel Motloch                   \\
Tony Mroczkowski                \\
Suvodip Mukherjee               \\
Johanna Nagy                    \\
Pavel Naselsky                  \\
Federico Nati                   \\
Paolo Natoli                    \\
Michael Niemack                 \\
Elena Orlando                   \\
Francesco Piacentini            \\
Nicolas Ponthieu                \\
Giuseppe Puglisi                \\
Benjamin Racine                 \\
Christian Reichardt             \\
Christophe Ringeval             \\
Karwan Rostem                   \\
Anirban Roy                     \\
Jose-Alberto Rubino-Martin      \\
Maria Salatino                  \\
Benjamin Saliwanchik            \\
Neelima Sehgal                  \\
Sarah Shandera                  \\
Erik Shirokoff                  \\
An\v{z}e Slosar                 \\
Tarun Souradeep                 \\
Suzanne Staggs                  \\
George Stein                    \\
Rashid Sunyaev                  \\
Aritoki Suzuki                  \\
Eric Switzer                    \\
Andrea Tartari                  \\
Grant Teply                     \\
Peter Timbie                    \\
Matthieu Tristram               \\
Caterina Umilt\`{a}             \\
Vincent Vennin                  \\
Licia Verde                     \\
Patricio Vielva                 \\
Benjamin Wallisch               \\
Benjamin Wandelt                \\
Scott Watson                    \\
Rien van de Weygaert            \\
Edward J. Wollack               \\
Siavash Yasini
%Martin White    \\
\end{multicols}
%\end{minipage}
}

%\newpage
\Large  {\centerline {Affiliations}}

\begin{multicols}{2}
\raggedright
\scriptsize {
%\footnotesize {
1. APC, Univ Paris Diderot, CNRS/IN2P3, CEA/lrfu, Obs de Paris, Sorbonne Paris Cit\'e, France.  \\
2. California Institute of Technology.  \\
3. Canadian Institute for Theoretical Astrophysics, University of Toronto, Canada.  \\
4. Cardiff University School of Physics and Astronomy.  \\
5. Carnegie Melon University.  \\
6. Center for Computational Astrophysics, Flatiron Institute.  \\
7. Columbia University.  \\
8. Cornell University.  \\
9. Department of Astronomy \& Astrophysics and Dunlap Institute, University of Toronto, Canada.  \\
10. Ecole Normale Superieure, Paris, France.  \\
11. European Space Astronomy Centre.  \\
12. Harvard-Smithsonian Center for Astrophysics.  \\
13. INAF-Istituto di Radioastronomia and Italian ALMA Regional Centre, Italy.  \\
14. INAF-Osservatorio Astronomico di Padova, Italy.  \\
15. Institut d'Astrophysique de Paris, CNRS and Sorbonne Universit\'e, France.  \\
16. Institut d'Astrophysique Spatiale, CNRS, Univ. Paris-Sud, Universit\'e Paris-Saclay, France.  \\
17. Institute for Advanced Study, Princeton.  \\
18. Instituto de F\'isica de Cantabria (CSIC-Universidad de Cantabria), Spain.  \\
19. IRAP, Universit\'e de Toulouse, France.  \\
20. IRFU, CEA, Universit\'e Paris-Saclay, France.  \\
21. JBCA, University of Manchester.  \\
22. Jet Propulsion Laboratory, California Institute of Technology.  \\
23. Johns Hopkins University.  \\
24. Kavli Institute for Particle Astrophysics and Cosmology.  \\
\columnbreak
25. Kavli Institute for the Physics and Mathematics of the Universe (WPI).  \\
26. Lawrence Berkeley National Laboratory.  \\
27. NASA Goddard Space Flight Center.  \\
28. National Institute of Standards and Technology.  \\
29. National Radio Astronomy Observatory.  \\
30. Northwestern University.  \\
31. Princeton University.  \\
32. Rutgers University.  \\
33. San Diego Supercomputer Center, University of California, San Diego.  \\
34. School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram,  India.  \\
35. Simon Fraser University.  \\
36. Southern Methodist University.  \\
37. Space Sciences Laboratory, University of California, Berkeley.  \\
38. Stanford University.  \\
39. Universit\`a degli studi di Milano.  \\
40. University of British Columbia, Canada.  \\
41. University of California, Berkeley.  \\
42. University of California, Davis.  \\
43. University of California, San Diego.  \\
44. University of Florida.  \\
45. University of Illinois, Urbana-Champaign.  \\
46. University of Manchester.  \\
47. University of Michigan.  \\
48. University of Minnesota - Twin Cities.  \\
49. University of Oslo, Norway.  \\
50. University of Pennsylvania.  \\
51. University of Southern California.  \\
52. University of Wisconsin - Madison.  \\
53. Villanova University.  \\
}
\end{multicols}

\end{document}
