\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,times}
\usepackage{color}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{cite}
\usepackage{color}
\usepackage{longtable}

\usepackage{natbib}
\usepackage[pdftex,
 pdfauthor={PICO Systematics Working Group},
 pdftitle={PICO Systematic Error Report},
 pdfdisplaydoctitle=True]{hyperref}

\title{Probe of Inflation and Cosmic Origins (PICO) Systematic Errors and their Mitigation} 

\author{PICO Systematic Working Group: Brendan Crill, Ranajoy Banerji, \\ Colin Bischoff, Julian Borrill, 
Jacques Delabrouille, Joy Didier, Shaul Hanany, Eric Hivon, \\Brad Johnson, Paolo Natoli, Maurizio Tomasi, Andrea Zonca, et al.}
% define formatting
%\pagestyle{empty}
\parindent=0pt
\topmargin=0.in \headheight=0in \headsep=-0.1in \textheight=9.2in
\textwidth=6.5in \oddsidemargin=0in

\usepackage{array}
\usepackage[table]{xcolor}   


\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{K}[1]{>{\raggedright\centering\arraybackslash}m{#1}}


\newcommand\PRL{{\it Phys.~Rev.~Lett.}}
\newcommand\prl{{\it Phys.~Rev.~Lett.}}
\newcommand\ApJ{{\it Ap.~J.}}
\newcommand\apj{{\it Ap.~J.}}
\newcommand\ApJL{{\it Ap.~J.~Lett.}}
\newcommand\apjl{{\it Ap.~J.~Lett.}}
\newcommand\ApJS{{\it Ap.~J.~Suppl.}}
\newcommand\apjs{{\it Ap.~J.~Suppl.}}
\newcommand\PR{{\it Phys.~Rev.}}
\newcommand\PL{{\it Phys.~Lett.}}
\newcommand\MNRAS{{\it MNRAS}}
\newcommand\mnras{{\it MNRAS}}
\newcommand\MNRASL{{\it MNRAS\ Lett.}}
\newcommand\AnA{{\it Astron.~Astrophys.}}
\newcommand\BAAS{{\it Bull.~Am.~Astron.~Soc.}}
\newcommand\NP{{\it Nucl.~Phys.}}
\newcommand\RMP{{\it Rev.~Mod.~Phys.}}
\newcommand\ARAA{{\it ARAA}}
\newcommand\prd{{\it Phys.~Rev.~D.}}
\newcommand\plb{{\it Phys.~Lett.~B.}}
\newcommand\ao{{\it Appl.~Optics}}
\newcommand\aap{{\it Astron.~Astrophys.}}
\newcommand\aaps{{\it Astron.~Astrophys.~Suppl.}}
\newcommand\pasp{{\it Proc.~Ast.~Soc.~Pac.}}
\newcommand\josa{{\it J.~Opt.~Soc.~Am.}}
\newcommand\phr{{\it Phys. Reports}}
\newcommand\aj{{\it Astronomical Journal}}
\newcommand\jcap{{\it JCAP}}
\newcommand\apss{{\it ApSS}}

\begin{document}
\bibliographystyle{unsrt}

  \maketitle 

\section{Introduction}

Here we list systematic errors that impact the polarization science of the PICO mission concept, describe methods in the literature for mitigating these systematics, and describe specific work we did for the PICO study.  In many cases, we attempted to translate the need for mitigating systematics by spacecraft/mission/instrument design or by measurement into rough requirements for a mission.

We relied a lot on previous thinking for the CORE and Litebird concepts.

\section{Review of Major Systematics}


\begin{center}
 \begin{longtable}{K{3cm} L{4.3cm} L{4.3cm} L{4.3cm}}
 \hline
\textbf{Name} & \textbf{Description} & \textbf{State-of-the-art} & \textbf{Additional Possible Mitigation} \\
 \hline
 \endhead
  \rowcolor{lightgray}
&  \textbf{Pair Differencing} & & \\
 Bandpass Mismatch & 
 Edges and shapes of the the spectral filters vary from detector to detector. leaks T $\to$ P, P $\to$ P leakage if the source's bandpass differs from calibrator's bandpass\cite{Hoang_2017} & Precise bandpass measurement\cite{Pajot_2010};
SRoll algorithm\cite{Planck_Lowell}; filtering technique\cite{CORE_systematics};   &
polarization modulation; full I/Q/U maps for individual detectors mitigates; \textbf{Current techniques may be adequate}  \\
Beam mismatch &
\\
Gain mismatch &
\\
\hline 
  \rowcolor{lightgray}
&  \textbf{Optics} & & \\
Instrumental Polarization Sky T$\to$P & 
\\
Instrumental emission & 
\\
Cross-polarization &
\\
Sidelobes: Reflector Spillover & & &
See Sect.~\ref{sec:fsl}\\
Sidelobes: Stray reflections & & &
See Sect.~\ref{sec:fsl}
\\
Sidelobes: Diffraction & & &
See Sect.~\ref{sec:fsl}
\\
Beam ghosting & & &
See Sect.~\ref{sec:fsl}
\\
Scattering & & &
See Sect.~\ref{sec:fsl}
\\
Pointing systematic error
\\
Pointing jitter
\\
Chromatic beam shape
\\
\hline
  \rowcolor{lightgray}
&  \textbf{Detectors} & & \\
Time Response Accuracy and Stability  &
\\
Readout Cross-talk &
\\
Polarization Angle & & &
See Sect.~\ref{sec:angle}
\\
Gain Stability & & &
See Sect.~\ref{sec:gain}
\\
Detector Non-linearity &
\\
Residual correlated cosmic ray hits &
\\
ADC non-linearity &
\\
 \hline
 \rowcolor{white}
 \caption{\label{tbl:TechnologyGaps} \textbf{Technologies to be developed for exo-Earth direct imaging and characterization.}}
 \end{longtable}
 \end{center}

\section{PICO Reference Mission}

Here we describe the baseline mission concept used to simulate systematic errors.

\subsection{Simulation Tools}

We used toast, quickpol, and other tools.

\section{Highest Priority Systematics}

Here are more details about the three that worried us the most.

\subsection{Far Sidelobes}
\label{sec:fsl}

\subsection{Polarization Angle Calibration}
\label{sec:angle}

\subsection{Time-variable Gain Mismatch}
\label{sec:gain}

\section{Other Systematics}

\subsection{Pointing Accuracy and Reconstruction}

\section{Relation to Other Projects}

What possible overlap with S4.

\newpage

\bibliography{PICO_systematics_memo}

\end{document}


